---
title: "Getting Started With Commuter Flows"
author: "Alex Henoumont"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# CommuteRs Package

## Overview

The goal of commuteRs is to help analysts to study the journey to work for labor market in the United States. Some of the tools in this package aim to:  
  * Retrieve commuter flow data from the US Census LEHD Origin-Destination Employment Statistics Program  
  * Retrieve labor market statistics from The BLS Quarterly Census Earnings and Wages Program  
  * Clean up some of the data in a usable format  
  * Build API get and post requests from Mapquest, Google Directions, and TollGuru API  
  * Perform spatial analysis  
  * Preprocess data before modeling  
  * Model gravity equations for analysis  



## Prerequisites

To get started working with `commuteRs`, users should load the package along with the `tidyverse` package.  

```{r, echo=FALSE}
library(commuteRs)
library(tidyverse)
```

## Retrieving Scope of Analysis

For analysis of metropolitan area at the county level. `commuteRs` provides the `us_xwalk` dataset to quickly lookup counties of all US statisical areas. 

```{r}
data("us_xwalk")
```

After loading the data, counties can be found by filtering by the core-based statistical area name (`cbsaname`)

```{r}
atlanta_fips <- us_xwalk %>% 
  filter(str_detect(cbsaname, "Atlanta")) %>% 
  pull(fips)
```

If more psecific areas are needed. State wide crosswalk files can be retrieved from `state_xwalk()`. This function requires a single parameter for the state abreviation. This dataset is disaggregated down to the block code. Loading this file does take a little while.

```{r, eval=FALSE}
ga_xwalk <- state_xwalk("ga")
```

## Collecting Commuter Flows

```{r}
atlanta_flows <- get_commuter_flow("ga") %>% 
  aggregate_flow() %>% 
  filter(w_fips %in% atlanta_fips | h_fips %in% atlanta_fips)

atlanta_flows %>% glimpse()
```  

## Collecting Income Data from QCEW

```{r}
library(blscrapeR)

atlanta_qcew <- atlanta_fips %>% 
  map(~qcew_api(year=2017, qtr="A", slice="area", sliceCode=.x)) %>% 
  reduce(rbind) %>% 
  filter(agglvl_code == 70) #Code for total by county
```

